\documentclass{beamer}

\usepackage{macros}

\usetheme{Boadilla}
\usecolortheme{beaver}

\newcommand{\sectionframe}[1]{\begin{frame}\begin{center}{\Huge #1 }\end{center}\end{frame}}

\begin{document}

\author[A. Maurer]{Andrew Maurer}
\date{March 4, 2019}
\title[$\H^\bullet$ \& $\V$ for LSA]{Cohomology and Support Varieties for Classical Lie Superalgebras}

\begin{frame}
  \maketitle
\end{frame}

\begin{frame}{Overview}
  \tableofcontents
\end{frame}

\section{History}

%\sectionframe{History \\ \vspace{-.75em}{\footnotesize or} \\ {\small an extended motivating example}}
\sectionframe{History}

\pause
\begin{frame}{The Main Players}
  Support theory was pioneered by Jon Carlson here at UGA.
  \pause
  \begin{itemize}
    \item $k = \bar k$ field of characteristic $p > 0$,\pause
    \item $G$ = \textbf{finite group} with $p \mid |G|$, $p$-Lie algebra, pointed Hopf algebra, etc.\pause
    \item $\H^n(G;M) =$ cohomology groups. Can be multiplied using Yoneda product or cup product.\pause
    \end{itemize}
    \begin{theorem}[Evens, `61]
      \begin{itemize}
      \item The cohomology ring $\H^\bullet(G;k) = \Ext_{kG}^\bullet(k,k)$ is finitely generated.
      \item If $M$ is a finite-dimensional $kG$-module, $\Ext_{kG}^\bullet(M,M)$ is a Noetherian graded module for $\H^\bullet(G;k)$.
      \end{itemize}\pause
    \end{theorem}
    \emph{Idea for proof:} Reduce to Sylow subgroups using spectral sequence.
  \end{frame}

  \begin{frame}{Varieties}
    \pause
    \begin{definition}
      \begin{itemize}
        \item \emph{Cohomology Variety:} $\V_G = \Spec\left(\H^\bullet(G;k)\right)$\pause
        \item \emph{Support Variety:}
          \[
            \V_G(M) = \Z\left(\Ann_{\H^\bullet(G;k)}\left(\Ext_{kG}^\bullet(M,M)\right)\right) \subseteq \V_G
          \]
        \end{itemize}
      \end{definition}\pause
      Notice that $\V_G(M)$ is a conical subvariety.
      \begin{example}\pause
        If $G = \ZZ_p^r$, $p \neq 2$, then \[\H^\bullet(\ZZ_p^r;k) \cong k[x_1,\ldots,x_r] \otimes \Lambda(y_1,\ldots,y_r)\] with $\deg x_i = 2$, $\deg y_i = 1$. \\
        This implies $\H^{ev}(\ZZ_p^r;k) \cong k[x_1,\ldots,x_r]$ and thus $\V_{\ZZ_p^r} = \AA^r$.
      \end{example}
    \end{frame}

    \begin{frame}{Algebra $\leftrightarrow$ Geometry}
      \pause
      \begin{idea}
        Build a dictionary:
        \begin{center}
          \{Algebraic Data About $M$\} $\leftrightarrow$ \{Geometric Data About $\V_G(M)$\}
        \end{center}
      \end{idea}
      \begin{theorem}
        \begin{itemize}
        \item $M$ is injective if and only if $\V_G(M) = \{0\}$.\pause
        \item $c_G(M) = \dim \V_G(M)$\pause
        \item If $\V_G(M) = X \cup Y$ with $X \cap Y = \{0\}$, then $M = M_X \oplus M_Y$ with $\V_G(M_X) = X$ and $\V_G(M_Y) = Y$.\pause
        \end{itemize}
      \end{theorem}
      \pause Here $c_G(M)$ is the \emph{complexity}, meaning the \emph{rate of growth} of a minimal $kG$-projective resolution
      \[
        \ldots \to P_2 \to P_1 \to P_0 \to M \to 0
      \]
    \end{frame}

    \begin{frame}{Tensor Products}
      \pause
      \begin{theorem}[Tensor Product Theorem]
        Let $M$ and $N$ be $kG$-modules. The following varieties are equal:
        \[
          \V_G(M \otimes N) = \V_G(M) \cap \V_G(N)
        \]
      \end{theorem}
      \pause
      Tensor product theorems as above do not follow from general nonsense, and require explicit constructions.
      \pause
      \begin{definition}
        Let $E = \ZZ_p^r = \left< g_1,\ldots,g_r\right>$ be elementary Abelian.% The \emph{shifted subgroup}:
        \[
          \V_E^\# = \left<g_1 - 1, \ldots, g_r - 1\right> \subseteq kE
        \]
        And the \emph{rank variety} of a module $M$ is the subset of $\V_E^\#$
        \[
          \V_E^\#(M) = \left\{ v \in \V_E^\# \big| M\res_{\left<1 + v\right>} \text{ is not free }  \right\} \cup \left\{ 0 \right\}
        \]
        
      \end{definition}
    \end{frame}

    \begin{frame}{Tensor Products (cont)}
      \pause
      \begin{theorem}[Avrunin-Scott]
        There is an isomorphism $\V_E \cong \V_E^\#$, and under this isomorphism:
        \[
          \V_E(M) \cong \V_E^\#(M)
        \]
      \end{theorem}
      \pause
      \begin{theorem}[Quillen]
        The variety $\V_G$ may be expressed as the union of varieties for elementary Abelian subgroups.
        \[
          \V_G = \bigcup_{\substack{E \leq G \\ \text{el.ab.}}} \resmap_{G,E}^* \V_E
        \]
      \end{theorem}
      \pause
      \begin{corollary}
        \[\V_G(M \otimes N) = \V_G(M) \cap \V_G(N)\]
      \end{corollary}
    \end{frame}
\section[LSAs \& $\H^\bullet$]{New Situation and Motivating Results}

\sectionframe{New Situation {\small ~ \\ ~ \\ Classical Results}}

\begin{frame}{Lie Superalgebras}
  \pause
  \begin{definition}
    A Lie superalgebra $\g = \even{\g} \oplus \odd{\g}$ is a $\ZZ_2$-graded (complex) vector space with a bilinear bracket $[\cdot,\cdot]: \g \otimes \g \to \g$ satisfying: \pause
    \begin{itemize}
    \item $[x,[y,z]] = [[x,y],z] + (-1)^{\bar x \bar y} [y,[x,z]]$\pause
    \item $[x,y] + (-1)^{\bar x \bar y} [y,x] = 0$
    \end{itemize}
    for homogeneous $x,y,z \in \g$.
  \end{definition}\pause
  \begin{example}
    The degree-zero elements $\even{\g}$ form a Lie algebra.
  \end{example}

\end{frame}

\begin{frame}{Examples of Lie superalgebras}
  \begin{itemize}
    \pause
  \item $\gl(m|n) = $ all $(m+n) \times (m+n)$ matrices.
    \[
\even{\gl(m|n)} = \left(
  \begin{array}{c|c}
    A & 0 \\
    \hline
    0 & D
  \end{array}
\right)
\text{ and } \odd{\gl(m|n)} = \left(
  \begin{array}{c|c}
    0 & B \\
    \hline
    C & 0
  \end{array}
\right)
\]
\pause
  Bracket is given by $[X,Y] = X \circ Y - (-1)^{\bar X \bar Y} Y \circ X$.
  \pause\item $\sl(m|n)$ is the subsuperalgebra of $\gl(m|n)$ given by all matrices of \emph{supertrace} 0, i.e., those such that $\Tr A - \Tr D = 0$.
  \pause\item Those defined similarly to Lie algebras: linear transformations preserving certain forms on $\ZZ_2$-graded vector spaces.
  \end{itemize}
\pause
  The simple, complex, finite-dimensional Lie superalgebras were classified [Kac].
\end{frame}

\begin{frame}{Classical Lie superalgebras}\pause
  \begin{definition}
  A Lie superalgebra $\g = \even{\g} +\odd{\g}$ is \emph{classical} if there is a reductive algebraic group $\even{G}$ such that
  \begin{itemize}
  \item $\even{\g} = \Lie(\even{G})$, and
  \item An action $\even{G} \actson \odd{\g}$ differentiates to the adjoint action.
  \end{itemize}
  \end{definition}\pause
  \begin{example}
    The following are classical Lie superalgebras: $\gl(m|n)$, $\sl(m|n)$, $\mathfrak{osp}(m|n)$.
  \end{example}
\end{frame}

\begin{frame}{Modules for Lie superalgebras}\pause
  \begin{definition}
    A \emph{module} for $\g$ is a $\ZZ_2$-graded vector space $M = \even{M} \oplus \odd{M}$ with a homomorphism $\varphi: \g \to \gl(M)$. In this way $\g$ acts on $M$.
  \end{definition}\pause
  \begin{example}
    \begin{itemize}
    \item $\CC$ is the trivial $\g$-module.\pause
    \item $\g$ is a $\g$-module via the adjoint action.
    \end{itemize}
    
  \end{example}\pause
  A $\g$-module is really a graded module for $U_s(\g)$, the universal enveloping superalgebra:
  \[
    U_s(\g) = \mathcal{T}(\g) \bigg/ \left< \lambda \otimes \mu - (-1)^{\bar \mu \cdot \bar \lambda} \mu \otimes \lambda  - [\lambda, \mu]\right>.
  \]
\end{frame}

\begin{frame}{Wedges}\pause
  \begin{definition}
    The \emph{exterior product} of a $\g$-module $M = \even{M} \oplus \odd{M}$ is
    \[
      \superext{p}\left(M\right) = \mathcal{T}\left(M\right)\bigg/\left< \lambda \otimes \mu + (-1)^{\bar \mu \cdot \bar \lambda} \mu \otimes \lambda \right>
    \]\pause
    or
    \[
      \superext{p}\left(M\right) = \bigoplus_{i+j=p} \ext{i}\left(\even{M}\right) \otimes {S}^j\left(\odd{M}\right)
    \]\pause
 This is naturally a $\g$-module.   
  \end{definition}
\end{frame}

\begin{frame}{Relative cohomology I}\pause
  Relative cohomology fits into Hochschild's relative cohomology theory. \pause We use an explicit Koszul complex. \pause Let $\a \leq \even{\g}$ be a subsuperalgebra with $\even{\g} = \a \oplus \a^\perp$ as $\a$-modules. Define cochain groups
  \[
    C^p(\g,\a;M) = \Hom_\a\left(\superext{p}\left( \g/\a \right), M \right)
  \]\pause
  Equip this with differentials:
  \[
    d: C^{p}(\g,\a;M) \to C^{p+1}(\g,\a;M)
  \]
  \begin{align*}
    df(\w_0\wedge\ldots\wedge\w_p) = &\sum_i (-1)^{\tau_i(-)} \w_i . f(\w_0 \wedge \ldots \hat \w_i \ldots \wedge \w_p) \\
    &+ \sum_{i < j} (-1)^{\sigma_{i,j}(-)} f([\w_i,\w_j]\wedge \w_0 \ldots \hat \w_i \ldots \hat \w_j \ldots \wedge \w_p)
  \end{align*}
  Of course,
  \[
    d \circ d = 0
  \]
\end{frame}

\begin{frame}{Relative cohomology II}\pause
  \begin{definition}
    \[
      \H^p(\g,\a;M) = \frac{\ker\left(d:C^p(\g,\a;M) \to C^{p+1}(\g,\a;M)\right)}{\im\left(d: C^{p-1}(\g,\a;M) \to C^p(\g,\a;M)\right)}
    \]
    \pause Or
    \[
      \H^p(\g,\a;M) = \Ext^p_{(\g,\a)}(\CC,M)
    \]
  \end{definition}\pause
  \[
    \H^p(\g,\a;M) = \frac{\left\{0 \to M \to E_1 \to \ldots \to E_p \to \CC \to 0 \text{ which are $\a$-split}\right\}}{\sim}
  \]
\end{frame}

\begin{frame}{Relative cohomology III}\pause
  We can give the following direct sum of cohomology groups the structure of a graded $\CC$-algebra by Yoneda splice or tensor product:
  \[
    \H^\bullet(\g,\a;\CC) = \bigoplus_{p \in \ZZ} \H^p(\g,\a;\CC)
  \]\pause
  Under tensor product, the direct sum of cohomology groups for a module becomes a module for $\H^\bullet(\g,\a;\CC)$:
  \[
    \H^\bullet(\g,\a;M) = \bigoplus_{p \in \ZZ} \H^p(\g,\a; M).
  \]\pause
  As does
  \[
    \Ext^\bullet_{(\g,\a)}(M,M) = \bigoplus_{p \in \ZZ} \Ext^p_{(\g,\a)}(M, M).
  \]  
\end{frame}

\begin{frame}{A result of Fuks-Leites}\pause
  \begin{theorem}[Fuks-Leites]
    There are isomorphisms:
    \[
      \H^\bullet(\mathfrak{osp}(m|2n),0;\CC) \cong
      \begin{cases}
        \H^\bullet(\mathfrak{o}(m),0;\CC) \text{ if } m \geq 2n \\
        \H^\bullet(\mathfrak{sp}(2n),0;\CC) \text{ if } m < 2n
      \end{cases}
    \]
    \[
      \H^\bullet(\gl(m|n),0;\CC) \cong \H^\bullet(\gl(\max(m,n)),0;\CC)
    \]
      There's a similar statement for Lie superalgebras of type $G(3)$, $F(4)$, and $D(2,1;\alpha)$
    \end{theorem}\pause
    \begin{theorem}[Restated]
      In many cases, ordinary Lie superalgebra cohomology carries no geometric information.
    \end{theorem}
\end{frame}

\begin{frame}{A result of Boe-Kujawa-Nakano}\pause

  \begin{theorem}[Boe, Kujawa, Nakano 2006]
    Let $\g = \even{\g} \oplus \odd{\g}$ be a classical Lie superalgebra. The relative cohomology ring may be related to invariant theory
    \[
      \H^\bullet(\g,\even{\g};\CC) \cong S^\bullet(\odd{\g}^*)^{\even{G}}
    \]
    Therefore, $\H^\bullet(\g,\even{\g};\CC)$ is a finitely generated $\CC$-algebra.
  \end{theorem}\pause
  \begin{theorem}[Restated]
    Cohomology relative to the even subsuperalgebra carries geometric information, which is determined by geometric invariant theory.
  \end{theorem}
\end{frame}

\begin{frame}{Detecting Subalgebras}\pause
  The words \emph{stable} and \emph{polar} are GIT conditions of the action on $\even{G} \actson \odd{\g}$.\pause
  \begin{theorem}[Boe-Kujawa-Nakano]
    If $\g$ is a classical, simple Lie superalgebra with stable and polar action $\even{G} \actson \odd{\g}$, then there exists a Lie subsuperalgebra $\e \leq \g$ such that
    \[
      \H^\bullet(\g,\even{\g};\CC) \cong \H^\bullet(\e,\even{\e};\CC)^W
    \]
    where $W$ is a finite pseudoreflection group. Such a subsuperalgebra $\e$ is called a \emph{detecting subalgebra}.
  \end{theorem}
\end{frame}


\section{Spectral Sequence}
\sectionframe{Spectral Sequence}

\begin{frame}{Spectral sequence theorem}\pause

  \begin{theorem}
    Let $\g = \even{\g} \oplus \odd{\g}$ be a classical Lie superalgebra, $\a \leq \even{\g}$ a subalgebra, and $M$ a $\g$-module. There exists a spectral sequence $\{E_r^{p,q}(M)\}$ which computes cohomology and satisfies
    \begin{align*}
      E_2^{p,q}(M) \cong \H^p(\g,\even{\g};M) \otimes \H^q(\even{\g},\a;\CC) \Rightarrow \H^{p+q}(\g,\a;\CC).
    \end{align*}
    Moreover, when $M$ is finite-dimensional, $E_2^{\bullet,\bullet}(M)$ is a Noetherian $E_2^{\bullet,\bullet}(\CC)$-module.
  \end{theorem}
\pause
  \begin{corollary}
    The relative cohomology ring $\H^\bullet(\g,\a;\CC)$ is a finitely-generated $\CC$-algebra.
  \end{corollary}
\end{frame}

\begin{frame}{Filtration}\pause
  We filter the cochains in a way inspired by Hochschild and Serre:\pause
  \begin{itemize}
  \item Decompose:
    \[
      C^n(\g,\a;M) = \bigoplus_{i + j = n} C^i\left(\even{\g},\a;\Hom_\CC\left( \superext{j}\left(\g/\even{\g}\right),M\right)\right)
    \]\pause
  \item Filter:
    \[
      C^n(\g,\a;M)_{(p)} = \bigoplus_{\substack{i + j = n\\ i \leq n-p}} C^i\left(\even{\g},\a;\Hom_\CC\left( \superext{j}\left(\g/\even{\g}\right),M\right)\right)
    \]
    
  \end{itemize}
\pause
  We are guaranteed a spectral sequence of $\a$-modules:
  \[
    E_r^{p,q}(M) \Rightarrow \H^{p+q}(\g,\a;M).
  \]  
\end{frame}

\begin{frame}{ID Pages}\pause
  \begin{enumerate}
  \pause\item $E_0^{p,q}(M) \cong C^q(\even{\g},\a;\Hom_\CC(\superext{p}(\g/\even{\g}),M))$: Just a quotient.
    \vspace{0.2in}
  \pause\item $E_1^{p,q}(M) \cong \H^q(\even{\g},\a;\Hom_\CC(\superext{p}(\g/\even{\g}),M))$: Requires some algebraic gymnastics and a diagram chase.
    \vspace{0.2in}
  \pause\item $E_2^{p,q}(M) \cong \H^p(\g,\even{\g};M) \otimes \H^q(\even{\g},\a;\CC)$: This uses the fact that $\g$ is classical and a vanishing theorem for cohomology:
    
  \begin{align*}
    \Hom_\CC\left(\superext{p}(\g/\even{\g}),M\right) &= \Hom_{\even{\g}}\left(\superext{p}(\g/\even{\g}),M\right) \oplus V  \\ &= C^p(\g,\even{\g};M) \oplus V
  \end{align*}
\end{enumerate}
\end{frame}

\begin{frame}{ID Edge}
  \pause
  We have an edge homomorphism:
  \[
    {E_2^{\bullet,0}(M)} \to E_\infty^{\bullet,0}(M)
  \]\pause
  But recall $E_2^{\bullet,0}(M) \cong \H^\bullet(\g,\even{\g};M)$.
\pause
  \begin{theorem}
    The edge homomorphism $E_2^{\bullet,0}(M) \to E_\infty^{\bullet,0}(M)$ is induced by the restriction map
    \[
      \resmap:\H^\bullet(\g,\even{\g};M) \to \H^\bullet(\g,\a;M).
    \]
    
  \end{theorem}
\end{frame}


\section{Finite Generation}

\sectionframe{Finite Generation}

\begin{frame}{Finite generation}
  \pause
  \begin{theorem}
    When $M$ is finite-dimensional, $E_r^{\bullet,\bullet}(M)$ is a Noetherian $E_r^{\bullet,\bullet}(\CC)$-module for $2 \leq r \leq \infty$.
  \end{theorem}
  \pause
  \begin{corollary}
    $E_\infty^{\bullet,\bullet}(\CC)$ is a Noetherian $E_2^{\bullet,0}(\CC)$-module, and is thus finitely-generated.
  \end{corollary}
  \pause
  \begin{corollary}
    $\H^\bullet(\g,\a;\CC)$ is Noetherian $\H^\bullet(\g,\even{\g};\CC)$-module, and is therefore finitely-generated as a $\CC$-algebra.
  \end{corollary}
\end{frame}

\begin{frame}{Collapsing at $E_2$}\pause
  \begin{definition}
    Recall that a $\CC$-algebra $A$ is \emph{Cohen-Macaulay} if there is a polynomial subring $R$ such that $A$ is a finite and free $R$-module.
  \end{definition}
  \pause
  \begin{theorem}
   If the spectral sequence collapses at $E_2$, then $\H^\bullet(\g,\a;\CC)$ is a Cohen-Macaulay ring.
  \end{theorem}
 \pause
   This uses a rather serious result of Hochster-Roberts regarding invariants under a reductive group action being Cohen-Macaulay.
\end{frame}

\begin{frame}{Application}\pause
  \begin{theorem}
    Let $\g = \even{\g} \oplus \odd{\g}$ be a classical Lie superalgebra such that $\H^\bullet(\g,\even{\g};\CC)$ vanishes in odd degrees. Let $\l \leq \even{\g}$ be a standard Levi subalgebra (i.e., nonzero and generated by simple roots). The following hold:
    \begin{itemize}
    \pause\item Spectral sequence collapses at $E_2$.
    \pause\item $\H^\bullet(\g,\l;\CC)$ is Cohen-Macaulay.
    \pause\item $\kdim \H^\bullet(\g,\even{\g};\CC) = \kdim \H^\bullet(\g,\l;\CC)$.
    \end{itemize}
  \end{theorem}
  
  \pause The proof uses deep results from Kazhdan-Lusztig theory and Category $\O$ cohomology.

  \pause
\begin{example}
  This result applies to many $\g$. E.g., $\gl(m|n)$, $\sl(m|n)$, $\mathfrak{psl}(2n|2n)$, $\mathfrak{osp}(2m+1|2n)$, $\mathfrak{osp}(2m,2n)$, $P(4\ell - 1)$, $D(2,1;\alpha)$, $G(3)$, and $F(4)$.
\end{example}
\end{frame}

\section{Geometry}
\sectionframe{Geometry}

\begin{frame}{Cohomology varieties} \pause
  To do geometry, we need a finitely-generated commutative subring. As in Friedlander-Parshall, we use the even cohomology groups:
  \[
    \H^{ev}(\g,\a;\CC) = \bigoplus_{n \geq 0} \H^{2n}(\g,\a;\CC).
  \]
  \pause
  \begin{definition}
    The \emph{relative cohomology variety} of $\g$ relative to $\a$ is
    \[
      V_{(\g,\a)}(\CC) = \maxspec\left(\H^{ev}(\g,\a;\CC)\right).
    \]
    
  \end{definition}
\end{frame}

\begin{frame}{Support varieties}\pause
  A $\g$-module $M$ determines a $\H^\bullet(\g,\a;M)$-module $\Ext^\bullet_{(\g,\a)}(M,M)$.\pause This determines a variety
  \[
    \operatorname{Z}\left(\Ann_{\H^\bullet(\g,\a;\CC)}\Ext^\bullet_{(\g,\a)}(M,M)\right) \subseteq V_{(\g,\a)}(\CC).
  \]\pause
  Call this the \emph{relative support variety} $V_{(\g,\a)}(M) \subseteq V_{(\g,\a)}(\CC)$.
\end{frame}

\begin{frame}{Rank Varieties}\pause
  \begin{definition}
    For $\g$ classical, $M$ a $\g$-module, define the \emph{rank variety} of $M$ to be
    \[
      \V_{(\g,\even{\g})}^\#(M) = \left\{\even{G}.x \big| \even{G}.x \text{ is closed,} x \in \odd{\g}\text{, and } M\res_{\left<x\right>} \text{ is not projective} \right\} \cup \{ 0\}
    \]
  \end{definition}\pause
  \begin{definition}
    For $\g$ simple, classical, stable, and polar, and $M$ a $\g$-module, define the \emph{BKN rank variety} to be
    \[
      \V_{(\g,\even{\g})}^{rank}(M) = \{x \in \odd{\e} \mid M \res_{\left<x\right>} \text{ is not projective}\} \cup \{0\}
    \]    
  \end{definition}\pause
  \begin{conjecture}
    When both varieties exist, $\V_{(\g,\even{\g})}^{rank}(\CC) \cong \V_{(\g,\even{\g})}^\#(\CC)$, and under this association $\V_{(\g,\even{\g})}^{rank}(M) = \V_{(\g,\even{\g})}^\#(M)$.
  \end{conjecture}
\end{frame}

% \begin{frame}{Realization morphism and Natural Modules}\pause
%   We have the restriction map
%   \[
%     \H^\bullet(\g,\even{\g};\CC) \xrightarrow{\resmap} \H^\bullet(\g,\a;\CC)
%   \]\pause
%   And a corresponding \emph{realization morphism}
%   \[
%     V_{(\g,\even{\g})}(\CC) \xleftarrow{\Phi} V_{(\g,\a)}(\CC)
%   \]
% \pause
%   % \begin{definition}
%   %   We say a $\g$-module is \emph{natural} relative to $\a$ if
%   %   \[
%   %     \Phi(V_{(\g,\a)}(M)) = \Phi(V_{(\g,\a)}(\CC)) \cap V_{(\g,\even{\g})}(M).
%   %   \]
%   %   The subalgebra $\a$ is \emph{natural in $\g$} if every $\g$-module is natural relative to $\a$.
%   % \end{definition}
  
% \end{frame}

\begin{frame}{Tensor products}\pause
  We say a Lie superalgebra $\g$ \emph{satisfies the tensor product theorem} relative to $\a$ if
  \[
    V_{(\g,\a)}(M \otimes N) = V_{(\g,\a)}(M) \cap V_{(\g,\a)}(N)
  \]
  for all modules $M$ and $N$.
  \pause
  \begin{theorem}[Grantcharov-Grantcharov-Nakano-Wu]
    Let $\g$ be simple, classical, polar, and stable. Then $\g$ satisfies the tensor product theorem relative to $\even{\g}$.
  \end{theorem}
  [GGNW] Idea: Define rank varieties for detecting subalgebra, and prove
  \[
    \V_{(\g,\even{\g})}(M) \cong \V_{(\e,\even{\e})}^{rank}(M) / W
  \]
  
    \begin{example}
    The following Lie superalgebras satisfy the tensor product theorem: $\gl(m|n)$, $\sl(m|n)$, $\mathfrak{psl}(m|n)$, $\mathfrak{q}(n)$, $\mathfrak{osp}(m|n)$, $D(2,1;\alpha)$, $G(3)$, and $F(4)$.
  \end{example}
\end{frame}


\begin{frame}{Tensor products (cont)}
  \pause
  The [GGNW] techniques used to prove the tensor product theorem fundamentally rely on detecting subalgebra techniques. This does not obviously generalize to the general classical case.
  \pause
  \begin{conjecture}
    Let $\g$ be a classical Lie superalgebra. Then
    \[
      \V_{(\g,\even{\g})}(\CC) \cong \V_{(\g,\even{\g})}^\#(\CC)
    \]
    And under this identification, for every $\g$-module $M$
    \[
      \V_{(\g,\even{\g})}(M) = \V_{(\g,\even{\g})}^\#(M)
    \]
  \end{conjecture}
  \pause
  \begin{conjecture}[Kujawa-Nakano-Talian, 2014]
    The tensor product theorem holds for all classical Lie superalgebras.
  \end{conjecture}
  % \begin{theorem}
  %   Let $\g$ be a Lie superalgebra which satisfies the tensor product theorem relative to $\even{\g}$. Then \[\Phi(V_{(\g,\a)}(M \otimes N)) = \Phi(V_{(\g,\a)}(M)) \cap \Phi(V_{(\g,\a)}(N)).\]
  % \end{theorem}
\end{frame}

% \begin{frame}{Connectedness} \pause
%   We need to assume further $\g$ is \emph{stable} and \emph{polar}, some GIT conditions appearing in [Bagci-Kujawa-Nakano].

%   \pause
%   \begin{theorem}
%     Let $\g = \even{\g} \oplus \odd{\g}$ be classical, stable, and polar, with $\a \leq \even{\g}$ natural. Suppose $\Phi(V_{(\g,\a)}(M)) = X \cup Y$ with $X \cap Y = \{0\}$. Then there exist modules $M_1$ and $M_2$ with
%     \[
%       X = \Phi(V_{(\g,\a)}(M_1)) \text{ and } Y = \Phi(V_{(\g,\a)})(M_1).
%     \]
    
%   \end{theorem}
% \end{frame}

% \begin{frame}{Realizability}
%   \pause
%   \begin{theorem}
%     Let $\g = \even{\g} \oplus \odd{\g}$ be classical, stable, and polar, with $\a \leq \even{\g}$ natural. Let $X$ be a closed, conical, subvariety of $V_{(\g,\a)}(\CC)$. 
%   \end{theorem}
% \end{frame}

% \begin{frame}{What's next?}
%   \begin{enumerate}
%   \pause\item What happens when $\a \not\leq \even{\g}$? Are there cases when $\H^\bullet(\g,\a;\CC)$ is still finitely-generated?
%   \pause\item We saw that the spectral sequence collapses at $E_2$ implies $\H^\bullet(\g,\a;\CC)$ is CM. What about the converse? (It does for $p$-nilpotent Lie algebras, [Carlson-Nakano].)
%   \pause\item When is $\a$ natural?
%   \pause\item The dimension $\dim V_{(\g,\even{\g})}(M) = \atyp M$ for simple modules when $\g = \gl(m|n)$ [Boe-Kujawa-Nakano]. Is there a combinatorial interpretation for $\dim V_{(\g,\a)} M$ for simple $M$?
%   \end{enumerate}
% \end{frame}

% \begin{frame}[fragile]{Tensor Products Relative to $\a$}
%   When the tensor product theorem holds for $\g$ relative to $\even{\g}$
%   \begin{center}
%     \[
%     \begin{tikzcd}
%       \V_{(\g,\even{\g})}(M \cap N) \arrow[r,equals] & \V_{(\g,\even{\g})}(M) \cap \V_{(\g,\even{\g})}(N) \\
%       \V_{(\g,\a)}(M \cap N) \arrow[u,"\resmap^*"] & \V_{(\g,\a)}(M) \cap \V_{(\g,\a)}(N) \arrow[u,"\resmap^*"] \arrow[l,hook]
%    \end{tikzcd}
%    \]
%  \end{center}
%  Is the bottom morphism an equality? What techniques can be used to investigate this morphism?
% \end{frame}

\begin{frame}{Natural Subalgebras I}
\pause
  The restriction morphism $\resmap: \H^\bullet(\g,\even{\g};\CC) \to \H^\bullet(\g,\a;\CC)$ yields a finite-to-one realization morphism:
  \[
    \Phi: \V_{(\g,\a)}(\CC) \to \V_{(\g,\even{\g})}(\CC)
  \]
  \pause
  \begin{definition}
    For a classical Lie superalgebra $\g$, a subalgebra $\a \leq \even{\g}$ is \emph{natural} if
    \[
      \Phi\left(\V_{(\g,\a)}(M)\right) = \V_{(\g,\even{\g})}(M) \cap \Phi\left(\V_{(\g,\a)}(\CC)\right)
    \]
    
  \end{definition}
\end{frame}

\begin{frame}{Natural Subalgebras II}
  \pause
  \begin{theorem}
    Let $\a \leq \g$ be a natural subalgebra, with $M, N$ be $\g$-modules.
    \begin{itemize}
      \pause
    \item If $\g$ satisfies the tensor product theorem, then
      \[
        \Phi\left(\V_{(\g,\a)}(M \otimes N)\right) = \Phi(\V_{(\g,\a)}(M)) \cap \Phi(\V_{(\g,\a)}(N))
      \]
      \pause
    \item Let $\g$ be stable and polar, and $\Phi(\V_{(\g,\a)}(M)) = X_1 \cup X_2$ with $X_i$ closed conical and $X_1 \cap X_2 = \{0\}$. Then there exist modules $M_1$ and $M_2$ with $M = M_1 \oplus M_2$ and $\Phi(\V_{(\g,\a)}(M_i)) = X_i$.
      \pause
    \item Let $X$ be a closed conical subset of $\Phi(\V_{(\g,\a)}(\CC))$. There exists a $\g$-module $M$ with
      \[
        \Phi(\V_{(\g,\a)}(M)) = X
      \]
      
    \end{itemize}
  \end{theorem}
\end{frame}

\title[HBD Sarah]{}
\begin{frame}
  \centering
  \Huge Thank you!
\end{frame}

\end{document}
